Statistical Modeling of Galaxy Catalogues with Normalizing Flows

### 2022-06-15 src/tex/ms.tex
Moved paths and LSST err model to utils. Changed script folder structure.
Fixed modular script setup.
Added files missing from last commit

\begin{figure*}[t!]
    \script{plot_two_moons.py}
    \begin{centering}
        \includegraphics{figures/twomoons_example.pdf}
        \caption{
            A normalizing flow demonstrated on the two moons data set from \texttt{scikit-learn}.
            The two moons data on the left is mapped onto a two dimensional uniform distribution by the bijection $f$.
            The data are colored by quadrant to visualize their image in the latent space.
            You can sample the data distribution by sampling from the uniform distribution, and using $f^{-1}$ to map the back to the data space.
        }
        \label{fig:two-moons}
    \end{centering}
\end{figure*}

@@

\begin{figure*}[t!]
    \script{plot_main_galaxy_corner.py}
    \begin{centering}
        \includegraphics{figures/main_galaxy_corner.pdf}
        \caption{
            Distribution of the CosmoDC2 test set compared to the distribution learned by PZFlow.
            The close overlap of every pair-wise distribution demonstrates that PZFlow was able to learn the structure present in CosmoDC2 with high fidelity.
        }
        \label{fig:main-corner}
    \end{centering}
\end{figure*}

\begin{figure*}[t!]
    \script{plot_smooth_color_distribution.py}
    \begin{centering}
        \includegraphics{figures/smooth_color_distribution.pdf}
        \caption{
            Comparing the $r-i$ vs redshift distribution for galaxy samples from CosmoDC2 (left) and from the normalizing flow (right).
            The high-redshift galaxies in CosmoDC2 lie along discrete tracks in color space due to the discrete number of galaxy SED templates used in the simulation.
            PZFlow smooths over these discrete tracks, resulting in a color distribution that is smooth to high redshifts.
        }
        \label{fig:smooth-color-dist}
    \end{centering}
\end{figure*}

@@

\note{Figure of the posteriors.}

@@

\begin{figure*}[t!]
    \script{plot_conditional_galaxy_corner.py}
    \begin{centering}
        \includegraphics{figures/conditional_galaxy_corner.pdf}
        \caption{
            Distribution of the ellipticities and sizes of the galaxies in the CosmoDC2 test set compared to the distribution learned by PZFlow.
            The close overlap of every pair-wise distribution demonstrates that PZFlow was able to learn the structure present in CosmoDC2 with high fidelity.
        }
        \label{fig:conditional-corner}
    \end{centering}
\end{figure*}

@@

\begin{figure*}[t!]
    \script{plot_galaxy_losses.py}
    \begin{centering}
        \includegraphics{figures/galaxy_flow_losses.pdf}
        \caption{
            Training losses for the galaxy flows.
        }
        \label{fig:galaxy-flow-losses}
    \end{centering}
\end{figure*}

>>>>

\begin{figure*}[t!]
    \script{intro/plot_two_moons.py}
    \begin{centering}
        \includegraphics{figures/twomoons_example.pdf}
        \caption{
            A normalizing flow demonstrated on the two moons data set from \texttt{scikit-learn}.
            The two moons data on the left is mapped onto a two dimensional uniform distribution by the bijection $f$.
            The data are colored by quadrant to visualize their image in the latent space.
            You can sample the data distribution by sampling from the uniform distribution, and using $f^{-1}$ to map the back to the data space.
        }
        \label{fig:two-moons}
    \end{centering}
\end{figure*}

@@

\begin{figure*}[t!]
    \script{forward_model/plot_main_galaxy_corner.py}
    \begin{centering}
        \includegraphics{figures/main_galaxy_corner.pdf}
        \caption{
            Distribution of the CosmoDC2 test set compared to the distribution learned by PZFlow.
            The close overlap of every pair-wise distribution demonstrates that PZFlow was able to learn the structure present in CosmoDC2 with high fidelity.
        }
        \label{fig:main-corner}
    \end{centering}
\end{figure*}

\begin{figure*}[t!]
    \script{forward_model/plot_smooth_color_distribution.py}
    \begin{centering}
        \includegraphics{figures/smooth_color_distribution.pdf}
        \caption{
            Comparing the $r-i$ vs redshift distribution for galaxy samples from CosmoDC2 (left) and from the normalizing flow (right).
            The high-redshift galaxies in CosmoDC2 lie along discrete tracks in color space due to the discrete number of galaxy SED templates used in the simulation.
            PZFlow smooths over these discrete tracks, resulting in a color distribution that is smooth to high redshifts.
        }
        \label{fig:smooth-color-dist}
    \end{centering}
\end{figure*}

@@

\begin{figure}[t!]
    \script{forward_model/plot_posteriors.py}
    \begin{centering}
        \includegraphics{figures/posteriors.pdf}
        \caption{
            True redshift posteriors for a galaxy representing different amounts of information.
            The black posterior is calculated with the true magnitudes;
            the blue posterior is calculated after adding photometric errors;
            the orange posterior is calculated after adding photometric errors, but with the errors convolved during posterior calculation;
            the green posteriors is the same as the orange, except with the $u$ band marginalized over.
        }
        \label{fig:posteriors}
    \end{centering}
\end{figure}

@@

\begin{figure*}[t!]
    \script{forward_model/plot_conditional_galaxy_corner.py}
    \begin{centering}
        \includegraphics{figures/conditional_galaxy_corner.pdf}
        \caption{
            Distribution of the ellipticities and sizes of the galaxies in the CosmoDC2 test set compared to the distribution learned by PZFlow.
            The close overlap of every pair-wise distribution demonstrates that PZFlow was able to learn the structure present in CosmoDC2 with high fidelity.
        }
        \label{fig:conditional-corner}
    \end{centering}
\end{figure*}

@@

\begin{figure*}[t!]
    \script{forward_model/plot_galaxy_losses.py}
    \begin{centering}
        \includegraphics{figures/galaxy_flow_losses.pdf}
        \caption{
            Training losses for the galaxy flows.
        }
        \label{fig:galaxy-flow-losses}
    \end{centering}
\end{figure*}
